Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/Supplementary.tex
finishing up supp material

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
  rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.  The JP type is the same
  as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
  configuration rather than a
  disordered bilayer.  
%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type II, multilamellar phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type II, multilamellar phase under shear flow with
  shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type III, striated phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type III, striated phase under shear flow with
  shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{TG Flow Cases}}\par\medskip
\textbf{Type I, bilayer  phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under TG flow with shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, vesicle bilayer phase under TG flow with shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type II, multilamellar phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under TG flow with shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type III, striated phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under TG flow with shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:sttgraw}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
  rates $\dot\gamma=0.01$--$0.075$ ns$^{-1}$.  The JP type is the same
  as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
  configuration rather than a
  disordered bilayer.  
%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type II, multilamellar phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type II, multilamellar phase under shear flow with
  shear rates $\dot\gamma=0.025$--$0.075$ ns$^{-1}$.
%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type III, striated phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type III, striated phase under shear flow with
  shear rates $\dot\gamma=0.01$--$0.07$ ns$^{-1}$.
%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{TG Flow Cases}}\par\medskip
\textbf{Type I, bilayer  phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, bilayer phase under TG flow with flow 
  rates $\dot\gamma=0.013$--$0.05$ ns$^{-1}$.
%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, vesicle bilayer phase under TG flow with
  flow rates $\dot\gamma=0.005$--$0.044$ ns$^{-1}$. The JP type is the
  same as Figure~\ref{fig:ultgraw} except with a vesicle-shaped initial
  configuration rather than a disordered bilayer.
%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type II, multilamellar phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type II, multilamellar phase under TG flow with
  flow rates $\dot\gamma=0.025$--$0.069$~ns$^{-1}$.
%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type III, striated phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type III, striated phase under TG flow with flow
  rates $\dot\gamma=0.01$--$0.075$~ns$^{-1}$.
%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:sttgraw}
\end{figure}
